An Evaluation of Methods for Assessing Model Fit for Bayesian Diagnostic Classification Models

### 2024-06-27 manuscript/manuscript.qmd
final tweaks

Diagnostic classification models (DCMs; also known as cognitive diagnostic models [CDMs]) are a class of psychometric models where the latent traits are a set of fine-grained, discrete variables [@bradshaw-dcm; @delatorre-dcm; @rupp-dcm].
That is, rather than modeling a continuous scale score, DCMs estimate a respondent's proficiency or nonproficiency on a set of predefined skills.
These estimates result in a profile of skills on which each respondent is proficient.
These profiles offer stakeholders fine-grained results that are often more useful than an overall scale score.
For example, in educational assessment, DCMs provide results that are more instructionally relevant [@zhang-2023; @lim-2024].
Similarly, applying DCMs to psychological assessment allows researchers to directly model the presence or absence of a trait, rather than attempting to apply a cut point to a continuous scale [@liu-2020; @zhang-2024].

@@

crossing(generate = c("LCDM", "DINA"), estimate = c("LCDM", "DINA")) |> 
  mutate(abs = case_when(generate == estimate | estimate == "LCDM" ~ "No",
                         .default = "Yes"),
         rel = generate) |> 
  rename(`Generating model` = generate,
         `Estimated model` = estimate,
         `Absolute-fit flag` = abs,
         `Relative-fit preference` = rel) |> 
  flextable() |>
  merge_v(j = c("Generating model", "Relative fit preference")) |> 
  hline(i = 2) |> 
  width(width = 1.2) |> 
  theme_apa() |>
  line_spacing(part = "all") |>
  padding(padding.top = 5, padding.bottom = 5)
```

>>>>

Diagnostic classification models (DCMs; also known as cognitive diagnostic models [CDMs]) are a class of psychometric models where the latent traits are a set of fine-grained, discrete variables [@bradshaw-dcm; @delatorre-dcm; @rupp-dcm].
That is, rather than modeling a continuous scale score, DCMs estimate a respondent's proficiency or nonproficiency on a set of predefined skills.
These estimates result in a profile of skills on which each respondent is proficient.
These profiles offer stakeholders fine-grained results that are often more useful than an overall scale score.
For example, in educational assessment, DCMs provide results that are more instructionally relevant [@lim-2024; @thompson-2024; @zhang-2023].
Similarly, applying DCMs to psychological assessment allows researchers to directly model the presence or absence of a trait, rather than attempting to apply a cut point to a continuous scale [@liu-2020; @zhang-2024].

@@

crossing(generate = c("LCDM", "DINA"), estimate = c("LCDM", "DINA")) |> 
  mutate(abs = case_when(generate == estimate | estimate == "LCDM" ~ "No",
                         .default = "Yes"),
         rel = generate) |> 
  rename(`Generating model` = generate,
         `Estimated model` = estimate,
         `Absolute-fit flag` = abs,
         `Relative-fit preference` = rel) |> 
  flextable() |>
  merge_v(j = c("Generating model", "Relative-fit preference")) |> 
  hline(i = 2) |> 
  width(width = 1.2) |> 
  theme_apa() |>
  line_spacing(part = "all") |>
  padding(padding.top = 5, padding.bottom = 5)
```
